Summary Tables

### 2020-03-02 summary_tables.Rmd
Add captions

### Trip proportion Baseline
```{r}

kable(trip_prop)

@@

  print(kable(td, caption = paste("Distance table (mins) for ", city, "( ", count_people, " ) per person (people with trips)")))

@@

### Average distance Baseline
```{r}

kable(trip_dist)

>>>>

### Baseline trip proportion (%)
```{r}

kable(trip_prop, caption = 'Trip prop (%) for all case studies - only selected modes')

@@

  print(kable(td, caption = paste("Distance table (km) for ", city, "( ", count_people, " ) per person (people with trips)")))

@@

### Baseline average distance (km) for all case studies
```{r}

kable(trip_dist, caption = "Avg. distance per person (km) across all case studies")
